---
title       : Height-OK-Weight
subtitle    : Calculates Weight that is OK for your Height 
author      : Piolivie
job         : Wanna-be-Data-Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why Height-OK-Weight?

* Obesitas is a serious health problem in modern society. 
* Height-OK-Weight calculates lower and upper bound for normal weight of Adults
* OK means a Body Mass Index (BMI) between 18.5 and 24.9.
* BMI Categories: 
  * Underweight = <18.5
  * Normal weight = 18.5-24.9 
  * Overweight = 25-29.9 
  * Obesity = BMI of 30 or greater

--- .class #id 

## Disclaimer

* The information contained in this presentation is for general information purposes only. 
* Any reliance you place on such information is therefore strictly at your own risk.

--- .class #id 

## Normal Weight Calculation

* Lower Bound Weight
$$ \bbox[yellow,20px] 
{
Lower\,Bound\,Weight = 18.5 \times \Big(\frac{\,Heigth\,}{100}\,\,\Big)^2
}
$$
* Upper Bound Weight
$$ \bbox[yellow,20px]
{
Upper\,Bound\,Weight = 24.9 \times \Big(\frac{\,Heigth\,}{100}\,\,\Big)^2
}
$$

* Weight expressed in kilogram (kg) given a Height expressed in centimeter (cm)

* For example, adult person measuring 175 cm has healthy weight between 57 kg and 76 kg

--- .class #id 

## Demo

* R function calculating healthy weight range (okg) of adult person given his/her height (cm)
``` {r, eval=FALSE}
okg <- function(cm) {round(c(18.5,24.9)*(cm/100)^2,0)}
``` 
* Healthy weight of adult person measuring 175 cm
``` {r, eval=FALSE}
okg(cm=175)
``` 
* Is between 57 kg and 76 kg
``` {r, echo=FALSE}
okg <- function(cm) {round(c(18.5,24.9)*(cm/100)^2,0)}
okg(cm=175)
``` 
* Check it also out on http://piolivie.shinyapps.io/height-ok-weight/


